---
title: "Homework 1"
author: Chloe Chah
output: 
  github_document:
    toc: true
---

This is my solution to HW 1. 

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
  prob1_df =
    tibble(
     samp = rnorm(10),
     samp_gt_0 = samp > 0, 
     char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
     factor_vec = factor(c("low", "low", "low", "med", "med", "med", "med",      "high", "high", "high"))
    )
```

Take the mean of each variable in my data frame. 

```{r mean_pull_var}
  mean(pull(prob1_df, samp))
  mean(pull(prob1_df, samp_gt_0))
  mean(pull(prob1_df, char_vec))
  mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

Now I will show the code chunk that applies the as.numeric function to the logical, character, and factor variables.

```{r try_numeric, results = "hide"}
  as.numeric(pull(prob1_df, samp))
  as.numeric(pull(prob1_df, samp_gt_0))
  as.numeric(pull(prob1_df, char_vec))
  as.numeric(pull(prob1_df, factor_vec))
```

Now I will convert the vectors into different types of variables and multiply the results by the random sample. 

```{r multiply_rs}
  as.numeric(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp)
  as.factor(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp)
  as.numeric(as.factor(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp))
```

It seems like we can convert logical variables to numeric variables and multiply it by a numeric. However, if we can't convert the variable to a numeric variable such as for factor or character variables in the first place, then we also cannot multiply the product of as.numeric function by a numeric (we got an NA message when we tried to do this in the previous code chunk). This explains why we were got a warning/error message that says "argument is not numeric or logical: returning NA[1] NA" when we tried to take the mean of factor and character variables. On the other hand, it seems like R converted logical variables into 0s and 1s before taking the mean. 

## Problem 2

I've downloaded a package containing the penguins dataset directly through the console. I will then load the penguins dataset and run some in-line codes to get a short description of the dataset. 

```{r dataset_des}
  data("penguins", package = "palmerpenguins")
  
```

* The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)`  columns.
* There are a total of 8 variables in this dataset: `r names(penguins)`.
* There are 3 different species of penguins in the data set: `r unique(penguins$species, incomparables = FALSE)`.
* There are 3 different islands in the data set: `r unique(penguins$island, incomparables = FALSE)`.
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`mm with a standard deviation of `r sd(pull(penguins, flipper_length_mm),na.rm=TRUE)`mm. 
* The mean bill length is `r mean(pull(penguins, bill_length_mm), na.rm=TRUE)`mm with a standard deviation of `r sd(pull(penguins, bill_length_mm),na.rm=TRUE)`mm.
* The mean bill depth is `r mean(pull(penguins, bill_depth_mm), na.rm=TRUE)`mm with a standard deviation of `r sd(pull(penguins, bill_depth_mm),na.rm=TRUE)`mm.
* The mean body mass is `r mean(pull(penguins, body_mass_g), na.rm=TRUE)`g with a standard deviation of `r sd(pull(penguins, body_mass_g),na.rm=TRUE)`g.
* For more detailed descriptive information of the dataset, please refer to the values listed below: `r summary(penguins)`

Now I will create a scatterplot. 

```{r scatterplot}
  
  plot_df = tibble(
    x = penguins$bill_length_mm, 
    y = penguins$flipper_length_mm,
    z = penguins$species
  )
  
  plot_1 = ggplot(penguins, aes(x=bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
  
  plot_1
  
  ggsave("plot_1.pdf", height = 4, width = 6)
  
```



