---
title: "Homework 1"
author: Chloe Chah
output: 
  github_document:
    toc: true
---

This is my solution to HW 1. 

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
  prob1_df =
    tibble(
     samp = rnorm(10),
     samp_gt_0 = samp > 0, 
     char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
     factor_vec = factor(c("low", "low", "low", "med", "med", "med", "med",      "high", "high", "high"))
    )
```

Take the mean of each variable in my data frame. 

```{r mean_pull_var}
  mean(pull(prob1_df, samp))
  mean(pull(prob1_df, samp_gt_0))
  mean(pull(prob1_df, char_vec))
  mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

Now I will show the code chunk that applies the as.numeric function to the logical, character, and factor variables.

```{r try_numeric, results = "hide"}
  as.numeric(pull(prob1_df, samp))
  as.numeric(pull(prob1_df, samp_gt_0))
  as.numeric(pull(prob1_df, char_vec))
  as.numeric(pull(prob1_df, factor_vec))
```

Now I will convert the vectors into different types of variables and multiple the results by the random sample. 

```{r multiply_rs}
  as.numeric(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp)
  as.factor(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp)
  as.numeric(as.factor(pull(prob1_df, samp_gt_0))* pull(prob1_df, samp))
```

## Problem 2

I've downloaded a package containing the penguins dataset directly through the console. I will then load the penguins dataset and run some codes to get a short description of the dataset. 

```{r}
  data("penguins", package = "palmerpenguins")
  names(penguins)
  nrow(penguins)
  ncol(penguins)
  select(penguins, species) %>%
    group_by(species) %>%
    count()
  mean(pull(penguins, flipper_length_mm), na.rm=TRUE)
```

* The dataset contains 344 rows and 8 columns.
* There are a total of 8 variables in this dataset: "species", "island", "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", and "year". 
* There are three different species of penguins in the data set: Adelie, Chinstrap, and Gentoo. 
* The mean flipper length is 200.9152mm. 


